### 2012-07-18 paper_draft.tex
Introduced tables for survey-results. Made transition survey/openSNP easier.

There are substantial differences in terms of motivation, tested by Tukey's HSD test, between those people who have already been genotyped 
and those who are not planning on getting genotyped. The first group is likely to agree more strongly, on a five-point scale, with the following 
motivations for sharing genotypic information: because they want to help scientists (mean difference = 0.465, SE = 0.128), 
because they think of personal benefits (mean difference = 0.448, SE = 0.183) and because they are curious (mean difference = 1.159, SE = 0.193).

On the other hand, those people who are not planning on getting genotyped are more likely to agree with the following motivations 
for not sharing their data: because they fear discrimination (mean difference = 1.060, SE = 0.195), because they feel 
it is a breach of their privacy (mean difference = 0.821, SE = 0.225), because they fear negative consequences for their 
family members (mean difference = 0.733, SE = 0.21) or because they fear personalized advertising (mean difference = 0.848, SE = 0.208).

Similarly, those people who would share data with their DTC provider under any circumstances are likely to agree more strongly with 
the following motivations for sharing than those who would not share their data with their DTC company: because they want to help 
scientists (mean difference = 1.57, SE = 0.199), because they think of personal benefits (mean difference = 0.951, SE = 0.308), 
and because they are curious (mean difference = 1.99, SE = 0.321). In the case of curiosity as a motive, there is also a substantial difference between those who would share their data with their DTC company under the condition that it did not share the information and those who would not (mean difference = 1.116 SE = 0.344) as well as those who would share under any circumstances (mean difference = -0.874 SE = 0.182).

Those participants who are not willing to share data with their DTC company are likely to agree more strongly with the following motivations 
for not sharing their data when compared to those who would share their data with their DTC company under any circumstances: because they 
fear discrimination (mean difference = 1.52, SE = 0.322), because they feel it is a breach of their privacy (mean difference = 1.871, SE = 0.324), 
because they fear consequences for their family members (mean difference = 1.146, SE = 0.32) and because they fear personalized advertising (mean difference =  1.112, SE = 0.357). In the cases of fear of discrimination and fear of a breach of privacy, substantial differences between all three categories exist. Those who would share their data with their DTC company as long as it did not share the information agree less strongly than those who would not share the data with both fear of discrimination as a motive for not sharing (mean difference = -0.615, SE = 0.345) as well as fear of a breach of privacy (mean difference = -0.668, SE = 0.346). Those who would share their data under any circumstances are even less likely to agree with these motives than those who would share only if their DTC company did not share the information (fear of discrimination: mean value = -0.906, SE = 0.182; breach of privacy: mean difference = -1.203, SE = 0.183).

>>>>

There are substantial differences in terms of motivation, tested by Tukey's HSD test, between those people who have already been genotyped 
and those who are not planning on getting genotyped. The first group is likely to agree more strongly, on a five-point scale, with motivations for sharing genotypic information. On the other hand, those people who are not planning on getting genotyped are more likely to agree with the following motivations 
for not sharing their data. For easier comparison both of these groups are compared in table \ref{tab:motivations1}.

\begin{table}
\begin{tabular}{|l|l|l|}
\hline
& Turkey's HSD & \\ \cline{2-3}
& Mean difference & SE \\ \hline
\textbf{Motivation for sharing genotypings in participants} & & \\
\textbf{who are already genotyped} & & \\ \hline 
... curious & 1.159 & 0.193 \\ 
... want to help scientists & 0.465 & 0.128 \\
... for personal benefits & 0.448 & 0.183 \\ \hline
\textbf{Motivation for not sharing in participants} & & \\ 
\textbf{who are not planning to get genotyped} & & \\ \hline
... fear of discrimination & 1.06 & 0.195 \\
... breach of privacy & 0.821 & 0.225 \\
... fear of personalized advertising & 0.848 & 0.208 \\ 
... negative consequences for family members & 0.733 & 0.21 \\ \hline 
\end{tabular}
\caption{Differences in terms of motivation to share genotypings with the public in survey-participants who already received a genotyping compared to participants who are not planning to getting genotyped. }
\label{tab:motivations1}
\end{table}

\begin{table}
\begin{tabular}{|l|l|l|}
\hline
& Turkey's HSD & \\ \cline{2-3}
& Mean difference & SE \\ \hline
\textbf{Motivation for sharing genotypings in participants} & & \\
\textbf{who would share with their DTC provider} & & \\ \hline
... curiosity & 1.99 & 0.321 \\
... want to help science & 1.57 & 0.199 \\
... for personal benefits & 0.951 & 0.308 \\ \hline
\textbf{Motivation for sharing genotypings in participants} & & \\
\textbf{who would not share with their DTC provider} & & \\ \hline
... fear of discrimination & 1.52 & 0.322 \\
... fear of consequences for family members & 1.146 & 0.32 \\
... fear of personalized advertising & 1.112 & 0.357 \\ \hline
\end{tabular}
\caption{Differences in terms of motivations to share genotyping-data, comparison between participants who would share their genotyping data with their DTC provider with participants who would not share their data with their DTC provider.}
\label{tab:motivations2}
\end{table}

Similarly, those people who would share data with their DTC provider under any circumstances are likely to agree more strongly with 
the following motivations for sharing than those who would not share their data with their DTC company.
Those participants who are not willing to share data with their DTC company are likely to agree more strongly with the some motivations 
for not sharing their data when compared to those who would share their data with their DTC company under any circumstances, for an overview of the motivations of both groups, see table \ref{tab:motivations2}.

In the case of curiosity as a motive, there is also a substantial difference between those who would share their data with their DTC company under the condition that it did not share the information and those who would not (mean difference = 1.116 SE = 0.344) as well as those who would share under any circumstances (mean difference = -0.874 SE = 0.182).

In the cases of fear of discrimination and fear of a breach of privacy, substantial differences between all three categories exist. Those who would share their data with their DTC company as long as it did not share the information agree less strongly than those who would not share the data with both fear of discrimination as a motive for not sharing (mean difference = -0.615, SE = 0.345) as well as fear of a breach of privacy (mean difference = -0.668, SE = 0.346). Those who would share their data under any circumstances are even less likely to agree with these motives than those who would share only if their DTC company did not share the information (fear of discrimination: mean value = -0.906, SE = 0.182; breach of privacy: mean difference = -1.203, SE = 0.183).

These survey-results indicate that there is a definite interest in customers of DTC-companies to share their results with other scientists. We've created the web-platform openSNP to help DTC-customers share their genotyping results with scientists, for free and under the open Creative Commons Zero-license.
